Programming Assignment 2

### 2015-04-02 paper.tex
Updated presentation assignments

\subsubsection{Project Presentation}
NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER
SKYLER, SKYYYYLLLLEERRRRR, SKYLLLLERRR NOOOOOOOOOOOOOOOOOOOOO
\subsection{Skyler Manzanares}

@@

\subsubsection{Project Presentation}
lulz he ain't done a thing.  0\% for you

@@

\subsubsection{Project Presentation}
nuthin. no soup for you

>>>>

\subsubsection{Project Presentation}
Jonathan updated the project with accurate testing results

\subsection{Skyler Manzanares}

@@

\subsubsection{Project Presentation}
Skyler laid out the outline of the slides and filled in the description of all the neural networks. He also wrote the encoding section.

@@

\subsubsection{Project Presentation}
William's main contribution to the presentation was results.
